Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-19 reanalysis-4-outcome_analysis.qmd
debug

# Extract weights for each imputation
for (i in 1:n_imputations) {
  imputed_datasets[[i]]$iptw_weight <- ps_results$twang_results[[i]]$weights
}
```

@@

message("All models fitted successfully")
```

@@

```{r pool-results}
# Use mitools for robust pooling implementation
# MIcombine properly implements Rubin's rules with Barnard-Rubin adjustment
pooled_model <- MIcombine(models)

>>>>

# Extract weights for each imputation
# Ensure we don't exceed available PS results
n_ps_weights <- length(ps_results$twang_results)
if (n_ps_weights < n_imputations) {
  warning("Only ", n_ps_weights, " PS weight sets available for ", n_imputations, " imputations")
  stop("Mismatch between imputations and PS results. Ensure PS analysis was run with same number of imputations.")
}

for (i in 1:n_imputations) {
  imputed_datasets[[i]]$iptw_weight <- ps_results$twang_results[[i]]$weights
}
```

@@

message("All models fitted successfully")

# Verify we have the expected number of models
if (length(models) != n_imputations) {
  stop("Model list has ", length(models), " models but expected ", n_imputations)
}

# Remove any NULL entries if they exist
models <- models[!sapply(models, is.null)]
if (length(models) == 0) {
  stop("No valid models to pool")
}

message("Ready to pool ", length(models), " models")
```

@@

```{r pool-results}
# Use mitools for robust pooling implementation
# MIcombine properly implements Rubin's rules with Barnard-Rubin adjustment

# Ensure models is a proper list for MIcombine
if (!is.list(models)) {
  stop("Models must be a list")
}

# Check that all models have the same structure
if (length(models) > 1) {
  coef_names_first <- names(coef(models[[1]]))
  for (i in 2:length(models)) {
    if (!identical(names(coef(models[[i]])), coef_names_first)) {
      warning("Model ", i, " has different coefficients than model 1")
    }
  }
}

pooled_model <- MIcombine(models)
